CES analysis for Paul Brockway rebound paper

### 2016-02-16 Articles/Brockway_Rebound_2015/Brockway_2015.Rnw
Now uses aes for geom_hline.

<<Rebound-graph, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=4.5, fig.cap="Time-dependent rebound.">>=
ggplot(Rebound) + 
  geom_line(mapping=aes(x=Year, y=Re, group=Country, linetype=Country)) +
  geom_hline(y=1, color = "gray70", size=0.3) +
  scale_y_continuous(breaks=c(0, 1, 2, 3), limits=c(0, 3)) +
  scale_linetype_manual(values = c(3,2,1)) +
  xlab("") +
  ylab("Rebound") +
  xy_theme() +
  theme(legend.title=element_blank())
@

>>>>

<<Rebound-graph, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=4.5, fig.cap="Time-dependent rebound.">>=
ggplot(Rebound) + 
  geom_line(mapping=aes(x=Year, y=Re, group=Country, linetype=Country)) +
  geom_hline(mapping=aes(yintercept=1), color = "gray70", size=0.3) +
  scale_y_continuous(breaks=c(0, 1, 2, 3), limits=c(0, 3)) +
  scale_linetype_manual(values = c(3,2,1)) +
  xlab("") +
  ylab("Rebound") +
  xy_theme() +
  theme(legend.title=element_blank())
@
